Variation in distance between consecutive animal locations

### 2021-03-15 distributions_paper/rudolph_distributions.Rmd
add libraries and data
Making density plots

```{r}
library(data)
```

@@

>>>>

```{r}
library(tidyverse)
library(aracari)
library(stringr)
library(fitdistrplus)
library(cowplot)
library(RColorBrewer)
library(gt)

theme_set(theme_bw())
```

```{r}
aracari_df <- readRDS("aracari_df.RDS")
```

```{r}
# Which individuals will we conside? Need at least a certain number of data points to fit distributions
# Don't remove any yet, just make sure you make it clear how many data points you have for each

aracari_df %>% 
  dplyr::filter(dist != 0) %>% 
  group_by(id) %>% 
  tally()
```

@@

### I'll go first with just the distances between locations, might switch to net displacement or net squared displacement later. 
**Visualize the variation and distribution of these distances between locations**

```{r}

aracari_df %>% 
  dplyr::filter(dist != 0) %>% 
  ggplot(., aes((x = dist))) +
  geom_line(aes(x = dist, group = id), stat = "density", alpha = 0.4) +
  geom_line(stat = "density", color = "#1191d1", lwd = 1) +
  geom_vline(xintercept = 0, color = "grey") +
  geom_hline(yintercept = 0, color = "grey") +
  labs(y = "Density", x = "Distance in meters") +
  theme_classic()

```

```{r}
aracari_df %>% 
  dplyr::filter(dist != 0,
                fam_g != "unknown") %>%
  ggplot(., aes((x = dist))) +
  facet_wrap(~fam_g) +
  geom_line(aes(x = dist, group = id), stat = "density", alpha = 0.4) +
  # geom_line(stat = "density", color = "#1191d1", lwd = 1) +
  geom_vline(xintercept = 0, color = "grey") +
  geom_hline(yintercept = 0, color = "grey") +
  labs(y = "Density", x = "Distance in meters") +
  #theme_classic() +
  NULL

aracari_df %>% 
  dplyr::filter(dist != 0) %>% 
  ggplot(., aes((x = dist))) +
  geom_line(aes(x = dist, group = id), stat = "density", alpha = 0.4) +
  geom_line(stat = "density", color = "#1191d1", lwd = 1) +
  geom_vline(xintercept = 0, color = "grey") +
  geom_hline(yintercept = 0, color = "grey") +
  labs(y = "Density", x = "Distance in meters") +
  theme_classic()
```

```{r eval = FALSE, fig.width=12, fig.height=4}

zoom_dims <- c(110, 210, 0, 0.01)
annot_xy <- c(50, 250, 0.025, 0.045)

ind_dens_plot <- df %>%
  ggplot(., aes(x = mpm)) +
  geom_line(stat = "density", color = "red", lwd = 1) +
  geom_line(aes(x = mpm, group = id), stat = "density", alpha = 0.4) +
  geom_vline(xintercept = 0, color = "grey") +
  geom_hline(yintercept = 0, color = "grey") +
  geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[3]), color = "blue") +
  geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[4], yend = zoom_dims[4]), color = "blue") +
  geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[1], y = zoom_dims[3], yend = zoom_dims[4]), color = "blue") +
  geom_segment(aes(x = zoom_dims[2], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[4]), color = "blue") +
  ylim(0, 0.055) +
  xlim(0, 250) +
  labs(title = "Individual") +
  theme_classic()

ind_dens_plot +
  coord_cartesian(
    xlim = zoom_dims[1:2],
    ylim = zoom_dims[3:4]) +
  theme(title = element_blank()) -> ind_zoom

ind_dens_plot +
  annotation_custom(grob = ggplotGrob(ind_zoom), xmin = annot_xy[1] , xmax = annot_xy[2] , ymin = annot_xy[3] , ymax = annot_xy[4]) -> a

fam_dens_plot <- df %>%
  filter(., fam_g != "unknown") %>% 
  ggplot(., aes(x = mpm)) +
  geom_line(stat = "density", color = "red", lwd = 1) +
  geom_line(aes(x = mpm, group = fam_g), stat = "density", alpha = 0.4) +
  geom_vline(xintercept = 0, color = "grey") +
  geom_hline(yintercept = 0, color = "grey") +
  geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[3]), color = "blue") +
  geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[4], yend = zoom_dims[4]), color = "blue") +
  geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[1], y = zoom_dims[3], yend = zoom_dims[4]), color = "blue") +
  geom_segment(aes(x = zoom_dims[2], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[4]), color = "blue") +
  ylim(0, 0.055) +
  xlim(0, 250) + 
  labs(title = "Family") +
  theme_classic()

fam_dens_plot +
  coord_cartesian(
    xlim = zoom_dims[1:2],
    ylim = zoom_dims[3:4]) +
  theme(title = element_blank()) -> fam_zoom

fam_dens_plot +
  annotation_custom(grob = ggplotGrob(fam_zoom), xmin = annot_xy[1] , xmax = annot_xy[2] , ymin = annot_xy[3] , ymax = annot_xy[4]) -> b

plot_grid(a, b)

```
